Soss

### 2019-12-30 paper/paper.tex
edits

\usepackage[ruled]{algorithm2e} 
%\usepackage{parskip}
\usepackage{backnaur}
% \usepackage{jlcode}  
\usepackage{todonotes}
% \usepackage{textalpha}
\usepackage{tikz}
\usetikzlibrary{bayesnet}

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage[utf8x]{inputenc}
\usepackage{textgreek}
\usepackage{minted}

@@

            \node[obs] (y) {$y$};
            \node[det, above=of y] (yhat) {$\hat{y}$};
            \node[latent, left=of yhat] (epsi) {$\varepsilon_I$};
            \node[latent, above=of yhat] (alpha) {$\alpha$};
            \node[latent, right=of yhat] (epsj) {$\varepsilon_J$};
            \node[latent, left=of alpha] (sigi) {$\sigma_I$};
            \node[latent, right=of alpha] (sigj) {$\sigma_J$};
            \node[latent, below=of y] (sigma) {$\sigma$};

            \edge {sigi} {epsi};
            \edge {sigj} {epsj};
            \edge {sigma, yhat} {y};
            \edge {alpha} {sigi};
            \edge {alpha} {sigj};
            \edge {epsi,epsj} {yhat};

            \plate {I} {(y)(yhat)(epsi)} {$I$};
            \plate {J} {(y)(yhat)(epsj)(I.north east)} {$J$};

@@

    \begin{minted}{julia}
    m = @model I,J begin
        α ~ HalfCauchy()
        σi ~ HalfNormal(α)
        σj ~ HalfNormal(α)

        εi ~ Normal(0, σi) |> iid(I)
        εj ~ Normal(0, σj) |> iid(J)
        yhat = εz .+ εy'
        σ ~ HalfNormal()
        y ~ For(I,J) do i,j 
                Normal(yhat[i,j], σ)
            end
        end
    \end{minted} 
    \caption{}
    \end{subfigure}

    \caption{A plate diagram (a) and Soss encoding (b) for a two-way analysis of variance model}
    \label{}
\end{figure}

@@

\[
    \ell = \beta
    - 0.5 \alpha^{2} 
    - 0.5 \beta^{2}
    - \sigma^{2} 
    + \sum_{\left(j_{1}\right)=1}^{n} \left(
        - \log{\left(\sigma \right)} 
        - \frac{\log{\left(\pi \right)}}{2} 
        - \frac{\log{\left(2 \right)}}{2} 
        - \frac{\left({y}_{\left(j_{1}\right)} 
        - {\hat{y}}_{\left(j_{1}\right)}\right)^{2}}{2 \sigma^{2}}
        \right) 
    + \sum_{j_{1}=1}^{n} \left(
        - 0.005 {x}_{j_{1}}^{2} 
        - 3.0 
        - \frac{\log{\left(\pi \right)}}{2} 
        + \frac{\log{\left(2 \right)}}{2}
        \right) 
    - 2 \log{\left(\pi \right)} 
    - 1.38629436111989
\]

\[
  \ell =
  - 3.7 
  - 4.1 n 
  - \frac{ \alpha^{2} }{2}
  - \frac{\beta^2}{2}
  - \sigma^{2} 
  - n \log{\left(\sigma \right)} 
  - 0.005 \sum_{j_{1}=1}^{n} {x}_{j_{1}}^{2} 
  - \frac{1}{\sigma^2}\sum_{j_{1}=1}^{n} \left({y}_{j_{1}} 
  - {\hat{y}}_{j_{1}}\right)^{2}
\]

>>>>

\usepackage[ruled]{algorithm2e} 
%\usepackage{parskip}
\usepackage{backnaur}
% \usepackage{jlcode}  
\usepackage{todonotes}
\usepackage{alphabeta}
% \usepackage{textalpha}
\usepackage{tikz}
\usepackage{bookmark}
\usetikzlibrary{bayesnet}

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage[utf8]{inputenc}
% \usepackage{unicode-math}
\usepackage{textgreek}
\usepackage{minted}

@@

            \node[obs] (y) {$y$};
            \node[det, above=of y] (yhat) {$\hat{y}$};
            \node[latent, left=of yhat] (alpha) {$\alpha$};
            \node[latent, above=of yhat] (lambda) {$\lambda$};
            \node[latent, right=of yhat] (beta) {$\beta$};
            \node[latent, left=of lambda] (sigi) {$\sigma_I$};
            \node[latent, right=of lambda] (sigj) {$\sigma_J$};
            \node[latent, below=of y] (sigma) {$\sigma$};

            \edge {sigi} {alpha};
            \edge {sigj} {beta};
            \edge {sigma, yhat} {y};
            \edge {lambda} {sigi};
            \edge {lambda} {sigj};
            \edge {alpha,beta} {yhat};

            \plate {I} {(y)(yhat)(alpha)} {$I$};
            \plate {J} {(y)(yhat)(beta)(I.north east)} {$J$};

@@

    \begin{minted}{julia}
m = @model I,J begin
    λ ~ HalfCauchy()
    σI ~ HalfNormal(λ)
    σJ ~ HalfNormal(λ)

    α ~ Normal(0, σI) |> iid(I)
    β ~ Normal(0, σJ) |> iid(J)
    yhat = α .+ β'

    σ ~ HalfNormal()
    y ~ For(I,J) do i,j 
            Normal(yhat[i,j], σ)
        end
    end
    \end{minted} 
    \caption{}
    \end{subfigure}

    \caption{A plate diagram (a) and Soss encoding (b) for a two-way analysis of variance model.}
    \label{}
\end{figure}

@@

\[
\begin{aligned}
    \ell = 
       &- 3 \log{\left(2 \right)} 
        - 5 \log{\left(\pi \right)} 
    \\ &- σ^{2} 
        - 4 \log{\left(λ \right)} 
        - 2 \log{\left(λ^{2} + 1 \right)} 
        - \frac{σ_I^{2}}{λ^{2}} 
        - \frac{σ_J^{2}}{λ^{2}}
    \\ &+ \sum_{i=1}^{I} \left(- \log{\left(σ_I \right)} - \frac{\log{\pi }}{2} - \frac{\log{2 }}{2} - \frac{{α}_{i}^{2}}{2 σ_I^{2}}\right) 
    \\ &+ \sum_{j=1}^{J} \left(- \log{\left(σ_J \right)} - \frac{\log{\pi }}{2} - \frac{\log{2 }}{2} - \frac{{β}_{j}^{2}}{2 σ_J^{2}}\right) 
    \\ &+ \sum_{\substack{1 \leq i \leq I \\ 1 \leq j \leq J}} \left(- \log{\left(σ \right)} - \frac{\log{\pi }}{2} - \frac{\log{2 }}{2} - \frac{\left({y}_{ij} - {\hat{y}}_{ij}\right)^{2}}{2 σ^{2}}\right) 
\end{aligned}
\]

\[
    \begin{aligned}
    \ell =
    &- 7.8 - 0.92 I - 0.92 J - 0.92 I J 
    \\ &- 4 \log{λ } - 2 \log{\left(λ^{2} + 1 \right)} 
        - σ^{2} 
        - I J \log{σ } 
    \\ &- I \log{σ_I } - J \log{σ_J } - \frac{σ_I^{2}}{λ^{2}}  - \frac{σ_J^{2}}{λ^{2}}
    \\ &- \frac{1}{2 σ_I^{2}} \sum_{i=1}^{I} {α}_{i}^{2}
        - \frac{1}{2 σ_J^{2}} \sum_{j=1}^{J} {β}_{j}^{2}
        - \frac{1}{2 σ^{2}} \sum_{\substack{1 \leq i \leq I\\1 \leq j \leq J}} \left({y}_{ij} - {\hat{y}}_{ij}\right)^{2}
    \end{aligned}
\]
